Modular Curves

### 2020-01-28 paper.tex
final commit

\documentclass[a4paper]{article}

@@

\author{Micha\"el Maex}
\date{\today}
\title{Modular Curves}
\begin{document}

\maketitle
\pagebreak

\tableofcontents

\pagebreak

@@

This is the report of the journey of a student learning about elliptic curves. 
This report should be thought of as my notes while working my way through the first chapters of \emph{A First Course in Modular Forms} by Fred Diamond and Jerry Shurman\cite{diamondFirstCourseModular2005a}. 
This book is my main reference. 
Most of this report is paraphrasing this book, but I've added some details where I thought the book was lacking. 
I've also added some visual intuitions I developed to aid my understanding of this material. I hope potential readers will find these useful as well.

Unfortunately I did not get far enough into the subject to start studying more advanced subjects, due to the large amount of concepts, and relations between these concepts, that need to be understood first (the modular group, congruence subgroups, modular forms, complex tori, elliptic curves, modular curves, moduli spaces, \ldots). 
However this report should cover most if not all the prerequisites for understanding the more advanced topics.

@@

\begin{definition}
	The \emph{Modular group} are the $2\times 2$ matrices with integer coefficients and determinant $1$.
	 \[
		 \SL_2(\Z) =   \bigset{\begin{pmatrix} a& b\\ c& d \end{pmatrix}}{a, b, c, d \in \Z, ac - bd = 1}
	.\] 
\end{definition}
It can be shown that this is indeed a group and that it is generated by \[
	\begin{pmatrix}  1 & 1 \\ 0 & 1 \end{pmatrix} 
	\text{ and }
	\begin{pmatrix} 0 & -1 \\ 1 & 0 \end{pmatrix} 
.\] 
For a proof of this we refer to the appendices. 
We now define how this group acts on the complex half plane. 
\begin{definition}
	Let  $\gamma = \begin{pmatrix} a & b \\ c & d \end{pmatrix} $ be any element of $\SL_2\Z$ and $\tau$ be any element of $\mathcal{H} \cup \{\infty\} $.
	The multiplication of these two elements is defined as 
	\[
		\gamma(\tau) = \gamma \cdot \tau = \frac{a \tau + b}{ c \tau + d}
	.\] 
\end{definition}
Note that this group action is well defined. First we have to check that this every $\tau \in \mathcal{H} \cup \{\infty\}  $ gets mapped to another element of $\tau \in \mathcal{H} \cup \{ \infty\}$. 
Note that is is sufficient to check this for the action of the generators, which induce the maps \[
\tau \mapsto  \tau+1 \text{ and } \tau \mapsto \frac{-1}{\tau}
\]
for which it is obvious.
Further, we easily see that $I_2 \cdot \tau = \tau$. 
It also holds that for $\gamma = \begin{pmatrix} a & b \\ c & d \end{pmatrix} $ and $\beta = \begin{pmatrix} f & g \\ h & i \end{pmatrix} $: 
\begin{align*}
	\gamma \left( \beta \cdot  \tau\right) &=  \gamma\cdot \frac{f\tau + g}{h \tau + i} \\
					       &= \frac{a\left( \frac{f \tau + g}{h\tau + i} \right) + b}{c \left( \frac{f \tau + g}{h \tau + i} \right) + d} \\	
					       &= \frac{(af + bh)\tau + ga + bi}{(cf + dh) \tau + cg + di} \\
					       &= \begin{pmatrix} af + bh & ag + bi \\ cf + dh & cg + di \end{pmatrix} \cdot \tau \\
					       &= (\gamma \beta)\cdot \tau 
.\end{align*}

\subsection{Subgroups of the Modular Group} \label{sec:subgroups_of_the_modular_group}
Quite often it will be useful to restrict our focus to subgroups of the modular group. 
The type of subgroups of greatest interest are the so-called \emph{congruence subgroups}.
To define these we first have to define the so called \emph{principal congruence subgroups}.  
\begin{definition}
	For any $N \in \N$ we define the \emph{principal congruence subgroup of level $N$} to be \[
		\Gamma(N) = \bigset{\begin{pmatrix} a & b \\ c & d \end{pmatrix} \in \SL_2(\Z)}{\begin{pmatrix} a & b \\ c & d \end{pmatrix}  \equiv \begin{pmatrix} 1 & 0 \\ 0 & 1 \end{pmatrix}  (\mathrm{mod}\; N)}
	.\] 
\end{definition}

Further we define two subgroups
\begin{definition}
	For every $N \in \N$ we define $\Gamma_0$ and $\Gamma_1$ to be 
	\begin{align*}
		\Gamma_0(N) &= \bigset{\begin{pmatrix} a & b \\ c & d \end{pmatrix} \in \SL_2(\Z)}{\begin{pmatrix} a & b \\ c & d \end{pmatrix}  \equiv \begin{pmatrix} * & * \\ 0 & * \end{pmatrix}  (\mathrm{mod}\; N)} \\
		\Gamma_1(N) &= \bigset{\begin{pmatrix} a & b \\ c & d \end{pmatrix} \in \SL_2(\Z)}{\begin{pmatrix} a & b \\ c & d \end{pmatrix}  \equiv \begin{pmatrix} 1 & * \\ 0 & 1 \end{pmatrix}  (\mathrm{mod}\; N)}
	.\end{align*}
\end{definition} 
Note that 
\[
	\Gamma(N) \subset \Gamma_1(N) \subset \Gamma_0(N) \subset  \SL_2\Z
.\] 
We state without proof that $[\Gamma_1(N): \Gamma(N)] = N$, $[\Gamma_0 (N): \Gamma_1(N)]= \phi(N)$, $[\SL_2\Z: \Gamma_0(N)] = N \prod_{p \mathbin | \N}(1 + 1 /p)$. 
From this it follows that $[\Gamma(N): \SL_2\Z]= N^3 \prod_{p \mathbin | N} 1 - 1 /p^2$.
We will now give the general definition of \emph{congruence subgroups}. 
 \begin{definition}
	 A subgroup $\Gamma \subset \SL_2\Z$ is a \emph{congruence subgroup} if $\Gamma(N) \subset \Gamma$ for some $N \in \N$. In this case we say that $\Gamma$ is a congruence subgroup of level $N$. 
\end{definition}
\subsection{Defining Modular Forms}\label{sec:defining_modular_forms}

Some meromorphic functions $f:\mathcal{H}  \to \hat{\C}$ are in some sense invariant under the action of the modular group (or one of its subgroups). 
These functions are the \emph{modular forms}.

\begin{definition}
	Let $k$ be an integer. 
	A meromorphic function $f: \mathcal{H}  \to \C$ is \emph{weakly modular of weight $k$ } if \begin{equation} \label{eq:weakly_modular}
		f(\gamma(\tau)) = (ct + d)^{k}f(\tau)
	,\end{equation}
	for all $\gamma = \begin{pmatrix} a & b \\ c & d \end{pmatrix}  \in \SL_2(\Z)$ and $\tau \in \mathcal{H} $. 
\end{definition}

It's clearly enough so check \eqref{eq:weakly_modular} only for the generators of $\SL_2\Z$. I.e. check that
\begin{equation}\label{eq:sufficient_weakly_modular}
	f(\tau + 1) = f(\tau) \text{ and } f\left(-\frac{1}{\tau}\right)  = \tau^{k}f(\tau)
.\end{equation} 
From this we see that weakly modular functions are $\Z$ periodic.

@@

We are now ready to give the definition of a modular form. 
\begin{definition}\label{def:modular_form}
	Let $\Gamma$ be congruence subgroup of $\SL_2\Z$.
	A function $f: \mathcal{H}  \to \C$ is a \emph{modular form of weight $ k$ with respect to $\Gamma$} if 
	\begin{enumerate}
		\item $f$ is holomorphic on $\mathcal{H} $,
		\item $f$ is weakly modular of weight $k$ with respect to $\Gamma$, 
		\item $f[\gamma]_k$ is holomorphic at $\infty$ for every $\gamma \in \SL_2\Z$. 
	\end{enumerate}
	We denote the set of modular froms of weight $k$ with respect to $\Gamma$ as $\mathcal{M} _k(\SL_2\Z)$.

	If $\Gamma = \SL_2\Z$ we say simply that $f$ is a modular form of weight $k$. 
\end{definition}
The stament `holomorhic at $\infty$' deserves some explanation. 
One can show that any congruence subgroup contains a matrix of the form $\begin{pmatrix} 1 & k \\ 0 & 1 \end{pmatrix} $ ($\Gamma(N)$ contains  $\begin{pmatrix} 1 & n \\ 0 & 1 \end{pmatrix} $). 
If we choose this $k$ to be minimal we see that $f(\tau) = f(\tau + k)$. 
So $f$ is $k\Z$-periodic. It would be desirable if $f$ allowed a Fourrier expansion.  
There are many equivalent ways of defining `holomorphic at $\infty$', but for our purposes we will take this to mean that $f$ allows a Fourier expansion \footnote{The real picture behing holomopich at $\infty$ is that, due to $f$ being $k\Z$-periodic, $H$ can be 'rolled up' on the unit disk, where $\infty$ gets mapped to the center. In this picture  $f$ being holomorphic at $\infty$ means that  $f$ allows an extension which holomorphic on the center of the disk.}, i.e.\ \[
	f(\tau) = \sum_{n=0}^{\infty} a_n e^{n 2\pi i \tau / k}
,\]
for some $a_n \in \C$.
Another equivalent statement is that $\lim_{\im(\tau) \to \infty} f(\tau)$ exists and is finite.

@@

Finally we introduce a special type of modular called a cusp. The names comes from connection to modular curves that we will discuss later.
\begin{definition}\label{def:cusp}
	A \emph{cusp form} is a modular form $f$ (with respect to a congruence subgroup  $\Gamma$) such that for every  $\alpha \in \SL_2\Z$  the leading coefficient in its Fourier expansion is 0. 
	 The $\C$-vector space of cusp forms of weight $k$ is denoted $\mathcal{S} _k(\Gamma)$.
\end{definition}
Again, it is sufficient to check this for a representative for every coset $\alpha \Gamma$.

@@

\section{Lattices and Complex Elliptic Curves}
The main idea of this section is to construct tori by considering $\C$ as an additive group modulo a certain kind of embedding of $\Z^2$. This embedding of $\Z^2$ is called a lattice.  
\begin{definition}
	A \emph{lattice in $\C$} is additive subgroup $\Lambda = \omega_1 \Z \oplus \omega_2 \Z$ where $\omega_1, \omega_2 \in \C$ are linearly independent over $\R$ and $\omega_1 / \omega_2  \in \mathcal{H}$.
\end{definition}
\begin{definition}
	A \emph{complex torus} is a quotient of the complex plane by a lattice, \[
		\C / \Lambda = \bigset{z + \Lambda}{z \in \C} 
	.\] 
\end{definition}
This object is called as torus because of a geometric intuition. 
If one considers the parallelogram spanned by $\vec{\omega_1}, \vec{\omega_2}$ we see that the opposing edges are `glued' together. 
So topologically this space is homeomorphic to the torus (see \cref{fig:complex_torus}).

@@

The modular group tells us when two two lattices are equal. 
\begin{lemma}\label{lem:equality_of_lattices}
	Let $\Lambda = \omega_1\Z \oplus \omega_2\Z$ and $\Lambda' = \omega_1'\Z \oplus \omega_2\Z$ be two lattices. 
	Then $\Lambda = \Lambda'$ if and only if there exists an $\begin{pmatrix} a & b \\ c& d \end{pmatrix} \in \SL_2\Z$ such that \[
	\begin{pmatrix} \omega_1' \\ \omega_2' \end{pmatrix}  = 
	\begin{pmatrix} a & b \\ c& d \end{pmatrix} 
	\begin{pmatrix} \omega_1 \\ \omega_2 \end{pmatrix} 
	.\] 
\end{lemma}
\begin{proof}[Proof. (exercise 1.3.1)]
	\ltr
	We know that $\omega_1' \in \Lambda$, there there are $a, b \in \Z$ such that $\omega_1' = a \omega_1 + b \omega_2$. Similarly there are $c, d \in \Z$ such that $\omega_2' = c \omega_1 + d \omega_2$. 
	So  \[
	\begin{pmatrix} \omega_1' \\ \omega_2' \end{pmatrix}  = 
	\begin{pmatrix} a & b \\ c& d \end{pmatrix} 
	\begin{pmatrix} \omega_1 \\ \omega_2 \end{pmatrix} 
	.\] 
	We still have to argue that the matrix is in $\SL_2\Z$, i.e. has determinant 1. 
	Analogously we can find $f, g, h, i \in \Z$ such that \[
	\begin{pmatrix} \omega_1  \\ \omega_2 \end{pmatrix}  = 
	\begin{pmatrix} f & g \\ h& i \end{pmatrix} 
	\begin{pmatrix} \omega_1' \\ \omega_2' \end{pmatrix} 
	.\]
	Hence \[
	\begin{pmatrix} \omega_1 \\ \omega_2 \end{pmatrix}  = 
	\begin{pmatrix} f & g \\ h & i \end{pmatrix} 
	\begin{pmatrix} a & b \\ c & d  \end{pmatrix} 
	\begin{pmatrix} \omega_1 \\ \omega_2 \end{pmatrix} 
	.\]  
	From this it follows that the determinants must be either $1$ or $-1$. 
	We can see that is must be $1$ as the imaginary part of $\omega_1 / \omega_2$ and $\omega_1' / \omega_2'$ must be both positive.
	\rtl
	We can use the fact that the lattices are groups. We know that the $\Lambda'$ is generated by $\omega_1'$ and $\omega_2'$.
	We further know that $\omega_1' = a \omega_1 + b \omega_2$ so $\omega_1' \in \Lambda$. 
	Similarly we see that $\omega_2' \in \Lambda$.
	So $\Lambda' \subset  \Lambda$.

@@

A complex torus is a Riemann surface. This a not a report about Riemann surfaces, but to not completely shove everything under the rug I will quickly explain what a Riemann Surface is.
Recall that that smooth manifolds are spaces that are locally homeomorphic to $\R^{n}$ and equipped with a smoothly compatible atlas. 
In the same spirit Riemann surfaces are objects that look locally like $\C$ and equipped with an atlas that is holomorphicly compatible.
The complex tori are Riemann surfaces.

@@

In our study of complex tori, holomorphic maps between them are of great importance. 
In light of this we want to know how such a maps look like. It turns out they are linear transformations with some restrictions. 
\begin{proposition}
	Let $\phi: \C \ \Lambda \to \C \ \Lambda'$ be a holomorphic map between complex tori. 
	Then $\phi(z + \Lambda) = mz + b + \Lambda'$ for some $m, b \in \C$ such that $m \Lambda \subset  \Lambda'$. 
	The map is invertible if and only if $m \Lambda = \Lambda'$.
\end{proposition}
\begin{proof}
	The idea is to use topology to lift the map. As $\R^2 \simeq \C$ is the universal covering space of the torus we know that we can lift $\phi$ to a holomorphic map $\tilde \phi: \C / \Lambda \to \C$. We then can make this into a homolomorphism by first projecting $\C$ onto $\C / \Lambda$. We get a holomorphic map  $\tilde \phi: \C \to \C$.
	Take any $\lambda \in \Lambda$. 
	Then the map $f_\lambda(z) = \tilde\phi(z + \lambda) - \tilde \phi(z)$. We know that $f_{\lambda}$ is continous, but we also know that is must map to an element of $\Lambda'$, which is discrete, so it must be constant. 
	We can differentiate to find that $\tilde\phi'(z+ \lambda) = \tilde\phi'(z)$ for every $\lambda \in \Lambda$, hence it is  $\Lambda$ periodic.

@@

\subsection{Modular Forms and Complex Tori} \label{sec:modular_forms_and_complex_tori}
We now have a notion of \emph{morphisms} between complex tori. We can now ask ourselves the question how equivalence classes of isomorphic complex tori look like.
It turns out that every complex torus $\C / \Lambda$ is \emph{isomorphic} to a torus of the form $\C / \Lambda_\tau$, where $\Lambda_\tau = \tau \Z \oplus \Z$, for some $\tau \in  \mathcal{H}$. 
Indeed, by definition $\Lambda = \omega_1 \Z \oplus \omega_2 \Z$ for some $\omega_1, \omega_2 \in \C$ such that $\omega_1 / \omega_2 \in \mathcal{H} $. Let $\tau = \omega_1 / \omega_2$. 
Then $\frac{1}{\omega_1} \Lambda = \Lambda_\tau$. 
So the map  \[
\phi: \frac{\C}{ \Lambda} \to \frac{\C}{\Lambda_\tau}: z + \Lambda \mapsto \frac{z}{\omega_1} + \Lambda_\tau
\]
is an isomorphism.

>>>>

\documentclass[titlepage,a4paper]{article}

@@

\author{Micha\"el Maex}
\date{\today}
\title{Modular Curves}
\begin{document}
\pagenumbering{Alph}
    \maketitle
%\clearpage % end title page
\begingroup
  \pagestyle{empty}
  \null
  \newpage
\endgroup
\pagenumbering{arabic}
\tableofcontents
\pagebreak

@@

This report should be thought of as my notes while working my way through the first chapters of \emph{A First Course in Modular Forms} by Fred Diamond and Jerry Shurman\cite{diamondFirstCourseModular2005a}. 
This book is my main reference. 
Most of this report is citing theorems and definitions from this book and adapting the proofs to my own style. In doing so I've added some details where I thought the book was lacking and found slight variations of proofs that in my opinion are easier to understand.
I've also added some visual intuitions, which I developed to aid my understanding of this material, particularly in the sections about complex tori. 
I hope that any readers will find these useful as well.

Due to the large amount of concepts, and relations between these concepts, that need to be understood first (the modular group, congruence subgroups, modular forms, complex tori, elliptic curves, modular curves, moduli spaces, \ldots), I unfortunately did not get far enough into the subject to study the more advanced topics. 
However this report should cover most if not all the prerequisites for understanding the more advanced topics and I still had a lot of fun learning about the subject. 
The deadline for this report will definitely not be the end of learning about modular curves and related objects for me.

@@

\begin{definition}
	The \emph{Modular group} are the $2\times 2$ matrices with integer coefficients and determinant $1$.
	 \[
		 \SL_2(\Z) =   \bigset{\begin{pmatrix} a& b\\ c& d \end{pmatrix}}{a, b, c, d \in \Z, ac - bd = 1}
	.\] 
\end{definition}
It can be shown that this is indeed a group and that it is generated by \[
	\begin{pmatrix}  1 & 1 \\ 0 & 1 \end{pmatrix} 
	\text{ and }
	\begin{pmatrix} 0 & -1 \\ 1 & 0 \end{pmatrix} 
.\] 
For a proof of this we refer to the appendices. 
We now define how this group acts on the complex half plane. 
\begin{definition}
	Let  $\gamma = \begin{pmatrix} a & b \\ c & d \end{pmatrix} $ be any element of $\SL_2\Z$ and $\tau$ be any element of $\mathcal{H} \cup \{\infty\} $.
	The multiplication of these two elements is defined as 
	\[
		\gamma(\tau) = \gamma \cdot \tau = \frac{a \tau + b}{ c \tau + d}
	.\] 
\end{definition}
Note that this group action is well defined. First we have to check that this every $\tau \in \mathcal{H} \cup \{\infty\}  $ gets mapped to another element of $\tau \in \mathcal{H} \cup \{ \infty\}$. 
Note that is is sufficient to check this for the action of the generators, which induce the maps \[
\tau \mapsto  \tau+1 \text{ and } \tau \mapsto \frac{-1}{\tau}
\]
for which it is obvious.
Further, we easily see that $I_2 \cdot \tau = \tau$. 
It also holds that for $\gamma = \begin{pmatrix} a & b \\ c & d \end{pmatrix} $ and $\beta = \begin{pmatrix} f & g \\ h & j \end{pmatrix} $: 
\begin{align*}
	\gamma \left( \beta \cdot  \tau\right) &=  \gamma\cdot \frac{f\tau + g}{h \tau + j} \\
					       &= \frac{a\left( \frac{f \tau + g}{h\tau + j} \right) + b}{c \left( \frac{f \tau + g}{h \tau + j} \right) + d} \\	
					       &= \frac{(af + bh)\tau + ga + bj}{(cf + dh) \tau + cg + dj} \\
					       &= \begin{pmatrix} af + bh & ag + bj \\ cf + dh & cg + dj \end{pmatrix} \cdot \tau \\
					       &= (\gamma \beta)\cdot \tau 
.\end{align*}

\subsection{Subgroups of the Modular Group} \label{sec:subgroups_of_the_modular_group}
Quite often it will be useful to restrict our focus to subgroups of the modular group. 
The type of subgroups of greatest interest are the so-called \emph{congruence subgroups}.
To define these we first have to define the so called \emph{principal congruence subgroups}.  
\begin{definition}
	For any $N \in \N$ we define the \emph{principal congruence subgroup of level $N$} to be \[
		\Gamma(N) = \bigset{\begin{pmatrix} a & b \\ c & d \end{pmatrix} \in \SL_2(\Z)}{\begin{pmatrix} a & b \\ c & d \end{pmatrix}  \equiv \begin{pmatrix} 1 & 0 \\ 0 & 1 \end{pmatrix}  (\mathrm{mod}\; N)}
	.\] 
\end{definition}
Further we define two subgroups
\begin{definition}
	For every $N \in \N$ we define $\Gamma_0$ and $\Gamma_1$ to be 
	\begin{align*}
		\Gamma_0(N) &= \bigset{\begin{pmatrix} a & b \\ c & d \end{pmatrix} \in \SL_2(\Z)}{\begin{pmatrix} a & b \\ c & d \end{pmatrix}  \equiv \begin{pmatrix} * & * \\ 0 & * \end{pmatrix}  (\mathrm{mod}\; N)} \\
		\Gamma_1(N) &= \bigset{\begin{pmatrix} a & b \\ c & d \end{pmatrix} \in \SL_2(\Z)}{\begin{pmatrix} a & b \\ c & d \end{pmatrix}  \equiv \begin{pmatrix} 1 & * \\ 0 & 1 \end{pmatrix}  (\mathrm{mod}\; N)}
	.\end{align*}
\end{definition} 
One can easily verify that these three subsets do in fact define subgroups of $\SL_2\Z$. 
Note that 
\[
	\Gamma(N) \subset \Gamma_1(N) \subset \Gamma_0(N) \subset  \SL_2\Z
.\] 
We state without proof that $[\Gamma_1(N): \Gamma(N)] = N$, $[\Gamma_0 (N): \Gamma_1(N)]= \phi(N)$, $[\SL_2\Z: \Gamma_0(N)] = N \prod_{p \mathbin | \N}(1 + 1 /p)$. 
From this it follows that $[\Gamma(N): \SL_2\Z]= N^3 \prod_{p \mathbin | N} 1 - 1 /p^2$.
We will now give the general definition of \emph{congruence subgroups}. 
 \begin{definition}
	 A subgroup $\Gamma \subset \SL_2\Z$ is a \emph{congruence subgroup} if $\Gamma(N) \subset \Gamma$ for some $N \in \N$. In this case we say that $\Gamma$ is a congruence subgroup of level $N$. 
\end{definition}
\subsection{Defining Modular Forms}\label{sec:defining_modular_forms}

Some meromorphic functions $f:\mathcal{H}  \to \C \cup \{\infty\} $ are in some sense invariant under the action of the modular group (or one of its subgroups). 
These functions are the \emph{modular forms}.

\begin{definition}
	Let $k$ be an integer. 
	A meromorphic function $f: \mathcal{H}  \to \C$ is \emph{weakly modular of weight $k$ } if \begin{equation} \label{eq:weakly_modular}
		f(\gamma(\tau)) = (c\tau + d)^{k}f(\tau)
	,\end{equation}
	for all $\gamma = \begin{pmatrix} a & b \\ c & d \end{pmatrix}  \in \SL_2(\Z)$ and $\tau \in \mathcal{H} $. 
\end{definition}
	\Cref{eq:weakly_modular} behaves well with the multiplication in $\SL_2\Z$ in the sense that if \[
		\gamma = \begin{pmatrix} a & b \\ c & d \end{pmatrix} \text{ and }\beta = \begin{pmatrix} e & f \\ g & j \end{pmatrix} \text{ such that }
		\gamma \cdot  \beta = \begin{pmatrix} af + bh & ag + bj \\ cf + dh & cg + dj\end{pmatrix} 
	,\]
	it holds that 
	\[
		(c \beta\cdot \tau + d)\cdot (g \tau + j) = ((cf + dh) \tau + (cg + dj))
	.\] 
	So \[
		f(\gamma (\beta \tau)) = f ((\gamma \cdot  \beta)\tau)
	\] 
	is automatically satisfied.
In light of this it is clearly enough to check \eqref{eq:weakly_modular} only for the generators of $\SL_2\Z$. I.e. check that
\begin{equation}\label{eq:sufficient_weakly_modular}
	f(\tau + 1) = f(\tau) \text{ and } f\left(-\frac{1}{\tau}\right)  = \tau^{k}f(\tau)
.\end{equation} 
From this we see that weakly modular functions are $\Z$ periodic.

@@

We are now ready to give the definition of a modular form. 
\begin{definition}\label{def:modular_form}
	Let $\Gamma$ be congruence subgroup of $\SL_2\Z$.
	A function $f: \mathcal{H}  \to \C$ is a \emph{modular form of weight $ k$ with respect to $\Gamma$} if 
	\begin{enumerate}
		\item $f$ is holomorphic on $\mathcal{H} $,
		\item $f$ is weakly modular of weight $k$ with respect to $\Gamma$, 
		\item $f[\gamma]_k$ is holomorphic at $\infty$ for every $\gamma \in \SL_2\Z$. 
	\end{enumerate}
	We denote the set of modular forms of weight $k$ with respect to $\Gamma$ as $\mathcal{M} _k(\SL_2\Z)$.

	If $\Gamma = \SL_2\Z$ we say simply that $f$ is a modular form of weight $k$. 
\end{definition}
The statement `holomorphic at $\infty$' deserves some explanation. 
One can show that any congruence subgroup contains a matrix of the form $\begin{pmatrix} 1 & k \\ 0 & 1 \end{pmatrix} $ ($\Gamma(N)$ contains  $\begin{pmatrix} 1 & n \\ 0 & 1 \end{pmatrix} $). 
If we choose this $k$ to be minimal we see that $f(\tau) = f(\tau + k)$. 
So $f$ is $k\Z$-periodic. It would be desirable if $f$ allowed a Fourrier expansion.  
There are many equivalent ways of defining `holomorphic at $\infty$', but for our purposes we will take this to mean that $f$ allows a Fourier expansion\footnote{The real picture behind holomorphic at $\infty$ is that, due to $f$ being $k\Z$-periodic, $H$ can be `rolled up' on the unit disk, where $\infty$ gets mapped to 0. In this picture  $f$ being holomorphic at $\infty$ means that  $f$ allows an extension which holomorphic on the centre of the disk.}, i.e.\ \[
	f(\tau) = \sum_{n=0}^{\infty} a_n e^{n 2\pi i \tau / k}
,\]
for some $a_n \in \C$.
Another equivalent statement is that $\lim_{\im(\tau) \to \infty} f(\tau)$ exists and is finite.

@@

Finally we introduce a special type of modular form called a cusp. The names comes from connection to modular curves that I unfortunately did not get to study yet.
\begin{definition}\label{def:cusp}
	A \emph{cusp form} is a modular form $f$ (with respect to a congruence subgroup  $\Gamma$) such that for every  $\alpha \in \SL_2\Z$  the leading coefficient in its Fourier expansion is 0. 
	 The $\C$-vector space of cusp forms of weight $k$ is denoted $\mathcal{S} _k(\Gamma)$.
\end{definition}
Again, it is sufficient to check this for a representative for every coset $\alpha \Gamma$.

@@

\section{Lattices and Complex Elliptic Curves}
The main idea of this section is to construct tori by considering $\C$ as an additive group modulo a certain kind of embedding of $\Z^2$. This embedding of $\Z^2$ is called a lattice.  
\begin{definition}
	A \emph{lattice in $\C$} is additive subgroup $\Lambda = \omega_1 \Z \oplus \omega_2 \Z$ where $\omega_1, \omega_2 \in \C$ are linearly independent over $\R$ and $\omega_1 / \omega_2  \in \mathcal{H}$.
\end{definition}
\begin{definition}
	A \emph{complex torus} is a quotient of the complex plane by a lattice, \[
		\C / \Lambda = \bigset{z + \Lambda}{z \in \C} 
	.\] 
\end{definition}
This object is called a torus because topologically it is a torus. 
If one considers the parallelogram spanned by $\vec{\omega_1}, \vec{\omega_2}$ we see that the opposing edges are `glued' together. 
So topologically this space is homeomorphic to the torus (see \cref{fig:complex_torus}).

@@

The modular group tells us when two two lattices are equal. 
\begin{lemma}\label{lem:equality_of_lattices}
	Let $\Lambda = \omega_1\Z \oplus \omega_2\Z$ and $\Lambda' = \omega_1'\Z \oplus \omega_2'\Z$ be two lattices. 
	Then $\Lambda = \Lambda'$ if and only if there exists an $\begin{pmatrix} a & b \\ c& d \end{pmatrix} \in \SL_2\Z$ such that \[
	\begin{pmatrix} \omega_1' \\ \omega_2' \end{pmatrix}  = 
	\begin{pmatrix} a & b \\ c& d \end{pmatrix} 
	\begin{pmatrix} \omega_1 \\ \omega_2 \end{pmatrix} 
	.\] 
\end{lemma}
\begin{proof}[Proof. (exercise 1.3.1)]
	\ltr
	We know that $\omega_1' \in \Lambda$ there there are $a, b \in \Z$ such that $\omega_1' = a \omega_1 + b \omega_2$. 
	Similarly there are $c, d \in \Z$ such that $\omega_2' = c \omega_1 + d \omega_2$. 
	So  \[
	\begin{pmatrix} \omega_1' \\ \omega_2' \end{pmatrix}  = 
	\begin{pmatrix} a & b \\ c& d \end{pmatrix} 
	\begin{pmatrix} \omega_1 \\ \omega_2 \end{pmatrix} 
	.\] 
	We still have to argue that the matrix is in $\SL_2\Z$, i.e. has determinant 1. 
	Analogously we can find $f, g, h, i \in \Z$ such that \[
	\begin{pmatrix} \omega_1  \\ \omega_2 \end{pmatrix}  = 
	\begin{pmatrix} f & g \\ h& i \end{pmatrix} 
	\begin{pmatrix} \omega_1' \\ \omega_2' \end{pmatrix} 
	.\]
	Hence \[
	\begin{pmatrix} \omega_1 \\ \omega_2 \end{pmatrix}  = 
	\begin{pmatrix} f & g \\ h & i \end{pmatrix} 
	\begin{pmatrix} a & b \\ c & d  \end{pmatrix} 
	\begin{pmatrix} \omega_1 \\ \omega_2 \end{pmatrix} 
	.\]  
	From this it follows that the determinants must be either $1$ or $-1$. 
	We can see that is must be $1$ as the imaginary part of $\omega_1 / \omega_2$ and $\omega_1' / \omega_2'$ must be both positive.
	\rtl
	We can use the fact that the lattices are groups. We know that the $\Lambda'$ is generated by $\omega_1'$ and $\omega_2'$.
	We further know that $\omega_1' = a \omega_1 + b \omega_2$ so $\omega_1' \in \Lambda$. 
	Similarly we see that $\omega_2' \in \Lambda$.
	So $\Lambda' \subset  \Lambda$.

@@

A complex torus is a Riemann surface. This a not a report about Riemann surfaces, but to not completely shove everything under the rug I will quickly explain what a Riemann Surface is.
Recall that that smooth manifolds are spaces that are locally homeomorphic to $\R^{n}$ and equipped with a smoothly compatible atlas. 
In the same spirit Riemann surfaces are objects that look locally like $\C$ and equipped with an atlas that is holomorphically compatible.
The complex tori are Riemann surfaces.

@@

In our study of complex tori, holomorphic maps between them are of great importance. 
In light of this we want to know how such a maps look like. It turns out they are linear transformations with some restrictions. 
\begin{proposition}
	Let $\phi: \C / \Lambda \to \C / \Lambda'$ be a holomorphic map between complex tori. 
	Then $\phi(z + \Lambda) = mz + b + \Lambda'$ for some $m, b \in \C$ such that $m \Lambda \subset  \Lambda'$. 
	The map is invertible if and only if $m \Lambda = \Lambda'$.
\end{proposition}
\begin{proof}
	The idea is to use topology to lift the map. As $\R^2 \simeq \C$ is the universal covering space of the torus we know that we can lift $\phi$ to a holomorphic map $\tilde \phi: \C / \Lambda \to \C$. We get a holomorphic map  $\tilde \phi: \C \to \C$.
	Take any $\lambda \in \Lambda$. 
	Then the map $f_\lambda(z) = \tilde\phi(z + \lambda) - \tilde \phi(z)$. We know that $f_{\lambda}$ is continuous, but we also know that is must map to an element of $\Lambda'$, which is discrete, so it must be constant. 
	We can differentiate to find that $\tilde\phi'(z+ \lambda) = \tilde\phi'(z)$ for every $\lambda \in \Lambda$, hence it is  $\Lambda$ periodic.

@@

\subsection{Modular Forms and Complex Tori} \label{sec:modular_forms_and_complex_tori}
We now have a notion of \emph{morphisms} between complex tori. We can now ask ourselves the question how equivalence classes of isomorphic complex tori look like.
It turns out that every complex torus $\C / \Lambda$ is \emph{isomorphic} to a torus of the form $\C / \Lambda_\tau$, where $\Lambda_\tau = \tau \Z \oplus \Z$, for some $\tau \in  \mathcal{H}$. 
Indeed, by definition $\Lambda = \omega_1 \Z \oplus \omega_2 \Z$ for some $\omega_1, \omega_2 \in \C$ such that $\omega_1 / \omega_2 \in \mathcal{H} $. Let $\tau = \omega_1 / \omega_2$. 
Then $\frac{1}{\omega_2} \Lambda = \Lambda_\tau$. 
So the map  \[
\phi: \frac{\C}{ \Lambda} \to \frac{\C}{\Lambda_\tau}: z + \Lambda \mapsto \frac{z}{\omega_2} + \Lambda_\tau
\]
is an isomorphism.

This $\tau$ however may not be unique. Suppose that for some $\tau' \in \mathcal{H} $ the torus $\C / \Lambda_{\tau'}$ is also isomorphic to $\C / \Lambda$. 
In that case $\C / \Lambda_{\tau'}$ is also isomorphic to $\C / \Lambda_{\tau}$. 
Then for some $m$ it must be the case that $m \Lambda_{\tau'} = m\tau' \Z \oplus m \Z = \Lambda_\tau$. 
By \cref{lem:equality_of_lattices} this implies that there is some $\gamma = \begin{pmatrix} a & b \\ c& d \end{pmatrix}  \in \SL_2\Z$ \[
\begin{pmatrix} m\tau' \\ m \end{pmatrix}  = \begin{pmatrix} a & b \\ c& d \end{pmatrix}  \begin{pmatrix} \tau \\ 1 \end{pmatrix} 
.\] 
So \[
\tau' = \frac{m \tau'}{m} = \frac{a \tau + b}{c \tau + d} = \gamma\cdot \tau
.\] 
Hence we see that $\tau$ and $\tau'$ lie in the same orbit of the action of $\SL_2\Z$. 
Conversely $\C / \Lambda_\tau$ and $\C / \Lambda_{\gamma\cdot \tau}$ will always be isomorphic.
Hence we conclude that there is a bijective correspondence of isomorphism classes of complex tori and orbits of $\SL_2\Z$ acting on $\mathcal{H} $.\[
\begin{tikzcd}
	\left\{ \substack{\text{isomorphism classes} \\ \text{of complex tori}} \right\} \arrow[r, leftrightarrow] & 
	\mathcal{H} / \SL_2\Z\ 
\end{tikzcd}
.\] 
\subsection{Isogenies}
If we only consider the maps where the constant term $b$ is $0$ then these maps are clearly group morphisms between $\C / \Lambda$ and  $\C / \Lambda'$. 
As a result, the holomorphic group morphism between these two tori exists if and only if $m\Lambda = \Lambda'$ for some $m \in \C$. 
A nonzero holomorphic group morphism between complex tori is called an \emph{isogeny}.
